\section{The Seasons of the Year}

The Christian calendar is divided into seasons that follow the life of Jesus Christ.
We follow the calendar and the seasons to order our life to remember what our Lord has done for us.
The seasons follow the pattern of fasting and feasting, with each feast preceded by a fast.
In a fast, we prepare our hearts for the joy of the feast to come.

\begin{itemize}
\item The Fast of Advent
\item The Feast of Christmas
\item The Fast of Lent
\item The Feast of Easter
\end{itemize}

\subsection*{Advent}

Advent is the season of lights, and is celebrated over the four Sundays before Christmas Day, beginning either in the last week of November or the first week of December.
It celebrates the coming of the Lord Jesus, the light that has come into the world.
Advent is marked by the lighting of candles.
Each week on Sunday, a new candle is lit; during the week, the week's candles are lit whenever the family gathers to eat at the table.

\subsection*{Christmas}

The season of Christmas begins on Christmas Day, December 25th, and lasts 12 days ending with Epiphany, January 6.
The season is marked by the giving of gifts. The fifth candle of the advent wreath, the white candle, symbolizes Christ Jesus, and is lit along with the other advent candles at meals during this season.

\subsection*{Lent}

The season of Lent is the primary fast of the year, beginning on Ash Wednesday and lasting for 40 days, excluding Sundays, to end with Easter Sunday.
The season is marked by self-denial: it is fitting during this time to give up during this season something to which one is entitled.

There are always six Sundays in Lent.
The sixth Sunday in Lent is Palm Sunday, the beginning of Holy Week.
Holy Week concludes with Maundy Thursday, the commemoration of the Last Supper; Good Friday, the rememberance of the crucifixion of Jesus

\subsection*{Easter}

The season of Easter begins on Easter Sunday and ends with Pentecost.
The season celebrates the resurrection of Jesus and anticipates the giving of the Holy Spirit.

\subsection*{Ordinary Time}

The weeks of the year that are out of season are known as ordinary time.
There are as many as nine weeks between Epiphany and Ash Wednesday, and as many as twenty-nine weeks between Pentecost and the First Sunday of Advent.

\begin{centering}
    \begin{tabular}{cp{1.5cm}c cp{1.5cm}c}
    Year & Sundays After Epiphany & Easter Sunday & Year & Sundays After Epiphany & Easter Sunday \\\hline
    2025 & 8 & April 20 & 2063 & 8 & April 15 \\
    2026 & 6 & April 5  & 2064 & 6 & April 6 \\
    2027 & 5 & March 28 & 2065 & 5 & March 29 \\
    2028 & 8 & April 16 & 2066 & 7 & April 11 \\
    2029 & 6 & April 1  & 2067 & 6 & April 3 \\
    2030 & 8 & April 21 & 2068 & 9 & April 22 \\
    2031 & 7 & April 13 & 2069 & 7 & April 14 \\
    2032 & 5 & March 28 & 2070 & 5 & March 30 \\
    2033 & 8 & April 17 & 2071 & 8 & April 19 \\
    2034 & 7 & April 9  & 2072 & 7 & April 10 \\
    2035 & 5 & March 25 & 2073 & 5 & March 26 \\
    2036 & 7 & April 13 & 2074 & 8 & April 15 \\
    2037 & 6 & April 5  & 2075 & 6 & April 7 \\
    2038 & 9 & April 25 & 2076 & 8 & April 19 \\
    2039 & 7 & April 10 & 2077 & 7 & April 11 \\
    2040 & 6 & April 1  & 2078 & 6 & April 3 \\
    2041 & 8 & April 21 & 2079 & 9 & April 23 \\
    2042 & 6 & April 6  & 2080 & 7 & April 7 \\
    2043 & 5 & March 29 & 2081 & 5 & March 30 \\
    2044 & 8 & April 17 & 2082 & 8 & April 19 \\
    2045 & 7 & April 9  & 2083 & 6 & April 4 \\
    2046 & 5 & March 25 & 2084 & 5 & March 26 \\
    2047 & 7 & April 14 & 2085 & 8 & April 15 \\
    2048 & 6 & April 5  & 2086 & 5 & March 31 \\
    2049 & 8 & April 18 & 2087 & 8 & April 20 \\
    2050 & 7 & April 10 & 2088 & 7 & April 11 \\
    2051 & 6 & April 2  & 2089 & 6 & April 3 \\
    2052 & 9 & April 21 & 2090 & 8 & April 16 \\
    2053 & 6 & April 6  & 2091 & 7 & April 8 \\
    2054 & 5 & March 29 & 2092 & 5 & March 30 \\
    2055 & 8 & April 18 & 2093 & 7 & April 12 \\
    2056 & 6 & April 2  & 2094 & 6 & April 4 \\
    2057 & 9 & April 22 & 2095 & 9 & April 24 \\
    2058 & 7 & April 14 & 2096 & 8 & April 15 \\
    2059 & 5 & March 30 & 2097 & 5 & March 31 \\
    2060 & 8 & April 18 & 2098 & 8 & April 20 \\
    2061 & 7 & April 10 & 2099 & 7 & April 12 \\
    2062 & 5 & March 26 \\
\end{tabular}
\end{centering}
